Symmetric Peer-to-Peer Applications

### 2022-09-05 tpd-22.tex
...

In this section, we evaluate if our design meets its goals to ensure that all
peers (a) meet event deadlines, (b) advance in sync in real time, and (c) can
leave and join the network and remain symmetric.
%
We simulate an application varying the network topology, latency, and churn, as
well as the frequency and deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the correctness of unstable peers, such that they validate our
goals above, respectively.

Regarding (a), if a peer experiences a time travel, it means that it received
an event after its deadline.
We can count all time travel occurrences during the simulation.
%
Regarding (b), we can use an absolute simulation clock to track, in real time,
the pace of each peer in comparison to a reference peer most advanced in time.
%
Regarding (c), we can TODO specific peers and very that they TODO within a
short period of time.

@@

We simulate the application with $21$ peers using the mixed topology of
Figure~\ref{fig.topo}, with straight lines, long cycles, and short cycles.
%
In order to have an absolute clock to compare peers, we use a single machine
to simulate all peers, and output their logs to a single file.
We TODO the network latency and clock skew using TODO and TODO.

We now detail why we measure the properties above and how we instrument the
middleware implementation:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
We teak the middleware implementation to count time travel ticks.
We then measure the percentage of the sum of all time travels ticks over the to
the total simulation ticks (e.g., $1\%$, if all peers sum $1000$ time travel
ticks over $100k$ accumulated simulation ticks).
%
\item \textbf{Real-time pace of peers:}
We start each peer with a random delay of up to $10s$ to force a time mismatch,
and then verify if they synchronize and remain synchronized during the whole
simulation.
We teak the middleware to output its current tick every $100ms$.

>>>>

In this section, we evaluate if (and to what extent) our design meets its goals
to ensure that all peers (a) meet event deadlines, (b) advance in sync in real
time, and (c) can leave and join the network and remain symmetric.
%
We simulate an application varying the network topology, latency, and churn, as
well as the frequency and deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the correctness of unstable peers, such that they validate our
goals above, respectively.

Regarding (a), if a peer experiences a time travel, it means that it received
an event after its deadline.
We count all time travel occurrences during the simulation.
%
Regarding (b), we use an absolute simulation clock to track, in real time, the
execution pace of each peer in comparison to a reference peer most advanced in
time.
%
Regarding (c), we designate some peers to leave and join the network
periodically to assert that they catch up with the other peers in real time.

@@

We simulate the application with $21$ peers using the mixed topology of
Figure~\ref{fig.topo}, with peers organized in straight lines, long cycles, and
short cycles.
%
In order to have an absolute clock to compare peers, we use a single machine
to simulate all peers, and merge their logs into a single file constituting a
shared timeline.
%
We simulate the network latency and clock drift in software with random delays.

We now detail how we instrument the middleware implementation measure the
properties above:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
Every time a peer is ahead of time and needs to travel back, we output its id
and how much ticks it needs to travel back.
At the end, we measure the percentage of the sum of all time travel ticks over
the total simulation ticks.
As an example, if all peers sum $1000$ time travel ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
%
\item \textbf{Real-time pace of peers:}
We start each peer with a random delay of up to $10s$ to force a time mismatch.
We also force exaggerated clock drifts in random peers ($1ms$ every $1h$).
and then verify if they synchronize and remain synchronized during the whole
simulation.
We teak the middleware to output its current tick every $100ms$.
